---
title: "Report : Demographic analysis (eolpop)"
header-includes:
- \usepackage{booktabs}
output: pdf_document
params:
  intro: NA
  analysis: NA
  species: NA
  def_pop_text: NA
  vital_rates_mat: NA
  
  fatalities_unit: NA
  fatalities_input_type: NA
  fatalities_val1: NA
  fatalities_val2: NA
  
  pop_size_unit: NA
  pop_size_input_type: NA
  pop_size_val1: NA
  pop_size_val2: NA
  
  pop_growth_input_type: NA
  pop_growth_val1: NA
  pop_growth_val2: NA
  
  carrying_cap_unit: NA
  carrying_cap_input_type: NA
  carrying_cap_val1: NA
  carrying_cap_val2: NA
  
  PDF_plot: NA
  ECDF_plot: NA
  impact_plot: NA
  #trajectory_plot : NA
  
  time_horizon: NA
  impact_table: NA
  PrExt_table: NA 
  
  CI: NA
  QT: NA
  risk_A: NA
  impact_QT_table: NA
---

### Date of creation (dd/mm/yyyy): `r strftime(Sys.Date(), "%d/%m/%Y")`

### Type of analysis performed: `r paste(params$analysis)`

### Species: `r paste(params$species)`  

### Time horizon: `r paste(params$time_horizon)` years   
    
***
  
## Contexteof the study
`r paste(params$intro)`


## How the impacted population was defined/delineated
`r paste(params$def_pop_text)`


***

# Input parameters used

## Annual fatalities
*`r paste(params$fatalities_unit)`*  
`r paste(params$fatalities_input_type)`  
  
**`r paste(params$fatalities_val1)` `r paste(params$fatalities_val2)`**



## Population size
*`r paste(params$pop_size_unit)`*  
`r paste(params$pop_size_input_type)`  
  
**`r paste(params$pop_size_val1)` `r paste(params$pop_size_val2)`**



## Annual population growth rate
`r paste(params$pop_growth_input_type)`  
  
**`r paste(params$pop_growth_val1)` `r paste(params$pop_growth_val2)`**



## Carrying capacity
*`r paste(params$carrying_cap_unit)`*  
`r paste(params$carrying_cap_input_type)`  
  
**`r paste(params$carrying_cap_val1)` `r paste(params$carrying_cap_val2)`**


## Species vital rates
```{r, echo=FALSE}
kable(params$vital_rates_mat, align = "c", booktabs = TRUE)
```  



***


# Results

```{r, echo=FALSE}
library(kableExtra)
```

## Estimated impact after `r params$time_horizon` years
```{r, echo=FALSE}
kable(params$impact_table, align = "ccc", booktabs = TRUE)
```  
Note :  `r params$CI`% Confidence Interval (CI)  

## Value of impact at the `r params$QT`% quantile
(i.e., there is a risk of `r params$risk_A`% to under-estimate the real impact)
```{r, echo=FALSE}
params$impact_QT_table
```  

## `r paste("Probability of extinction after", params$time_horizon, "years")`
```{r, echo=FALSE}
kable(params$PrExt_table, align = "c", booktabs = TRUE)
```  



## Figure 1 : Probability density of the relative impact (after `r params$time_horizon` years)
```{r, echo=FALSE}
params$PDF_plot
```
Note : The median and confiance interval (`r params$CI`% CI) are shown on the graph.  

## Figure 2 : Cumulative probability density of the relative impact (after `r params$time_horizon` years)
```{r, echo=FALSE}
params$ECDF_plot
```
Note : Quantile = `r params$QT`%,  
(i.e., there is a risk of `r params$risk_A`% to under-estimate the real impact)

## Figure 3 : Relative impact across time
```{r, echo=FALSE}
params$impact_plot
```
Note : `r params$CI`% Confidence Interval (CI)  
